\chapter{Conclusion}
\label{chap:conclusion}

There is a strong need to develop structured, higher-level and type-safe abstractions and techniques for programming communications and interaction. This dissertation has presented a critical overview of web services standards and technologies existing today; deep analyzed the main issues inside the complex communication behaviour in a Web environment; introduced a pair of typed formalisms for interaction, one based on global descriptions and another an applied $\pi$-calculus, both using an extension of session types; implemented three scenarios from business environment offering web services in SJ; and compared the Session-Java performance with Java RMI and raw Java Sockets.

Global descriptions have been practiced in various engineering contexts for a long time. The presented work demonstrated its potential as a mathematically well-founded programming method, centring on type structures for communication. The presented formal theory of End-Point Projection helps to reach faultless behaviour of web services by ensuring us in well-formedness and conformance concepts.

Communication safety of distributed applications is guaranteed through a combination of static and dynamic type validation. My future work includes detailed analysis of how session-based programming can impact on the development of more complicated and large-scale applications (high-load web applications).

Preliminary benchmark results demonstrate the feasibility of session-based communication and session runtime architecture of SJ. Another interesting direction include the incorporation of different transports other than TCP into the session runtime (HTTP, HTTPs, SMTP, etc.).

The Master dissertation outcomes is a basis of the investigation of many further topics:

\begin{compactenum}
\item  performance optimization based on asynchronous I/O

\item  C10K problem\footnote{Ability of web servers to handle ten thousand simultaneously connected clients. More can be found \url{http://www.kegel.com/c10k.html}}

\item  integration to transports with order preservation message delivery \cite{dccp} or unambiguous unordered delivery \cite{amqp}.
\end{compactenum}